---
title: "Portfolio 9 Dot-and-Whisker Plot"
author: "Colin Li"
date: "4/20/2023"
output: github_document
---


People use multiple regression all the time. I always had a hard time plotting regression results and did not know another way to report it besides using tables. Then I discovered the Dot-and-Whisker Plot. The plot below shows 

```{r}

library(psych)
library(ggplot2)
library(haven)
library(data.table)
library(ggridges)
library(ggsci)
library(dotwhisker)
library(dplyr)
library(magrittr)
library(lm.beta)
library(tibble)
library(jtools)
library(scales)



```

```{r}

reg <- read_sav("C:/Users/Colin/Documents/reg.sav")

fear <- lm(fe ~ case_p + death_p + cv13 + risk_r + covrac, data = reg)

summary(fear)

distress <- lm(dis ~ case_p + death_p + cv13 + risk_r + covrac , data = reg)

psyh <- lm(psyh ~ case_p + death_p + cv13 + risk_r + covrac, data = reg)


```



```{r}

dwplot(fear) + theme_classic()


```


```{r}

dwplot(list(fear, distress, psyh), vline = geom_vline(
           xintercept = 0,
           colour = "grey60",
           linetype = 2
       ),
       vars_order = c("case_p", "death_p", "cv13", "risk_r", "covrac")) %>% 
  relabel_predictors(
        c(
            case_p = "County Covid Case %",
            death_p = "County Death Case %",
            cv13 = "Covid-Related Life Events",
            risk_r = "Race-Related Covid Risk",
           covrac = "Covid-Induced Racism"
        )) + theme_classic() + scale_color_aaas(name = "Outcome Variables",
        labels = c("Fear of Covid", "Psychological Distress", "Psychological Health Change")) + labs(title = "Predicting Negative Psychological Outcomes") + theme(plot.title = element_text(face = "bold", hjust = 0.5),  legend.position = c(0.5, 0.1),
        legend.justification = c(0, 0),
        legend.background = element_rect(colour = "grey80"),
        legend.title.align = .5
    )


```

The dots are the estimates, the lines indicate 95% confidence intervals. It might be easy to use covid-death percentages as an example. We can see death% predicts fear of covid but not the other 2 outcomes because the range includes 0. 
Obviously there are still problems. I wish the lines and dots could be thicker. I also hope that I can plot the standardized coefficients so the death% doesn't look so dramatic.

```{r}

reg <- reg[complete.cases(reg[ , c('case_p', 'death_p')]), ]


case_p.z <- (reg$case_p - mean(reg$case_p)) / sd(reg$case_p)

death_p.z <- (reg$death_p - mean(reg$death_p)) / sd(reg$death_p)

cv13.z <- (reg$cv13 - mean(reg$cv13)) / sd(reg$cv13)

risk_r.z <- (reg$risk_r - mean(reg$risk_r)) / sd(reg$risk_r)

covrac.z <- (reg$covrac - mean(reg$covrac)) / sd(reg$covrac)

fe.z <- (reg$fe - mean(reg$fe)) / sd(reg$fe)

dis.z <- (reg$dis - mean(reg$dis)) / sd(reg$dis)

psyh.z <- (reg$psyh - mean(reg$psyh)) / sd(reg$psyh)





```

```{r}

fear.z <- lm(fe.z ~ case_p.z + death_p.z + cv13.z + risk_r.z + covrac.z, data = reg)

distress.z <- lm(dis.z ~ case_p.z + death_p.z + cv13.z + risk_r.z + covrac.z , data = reg)

psyh.z <- lm(psyh.z ~ case_p.z + death_p.z + cv13.z + risk_r.z + covrac.z, data = reg)

dwplot(list(fear.z, distress.z, psyh.z), vline = geom_vline(
           xintercept = 0,
           colour = "grey60",
           linetype = 2), whisker_args = list(width = 0.2, size = 1), dot_args = list(size = 4), 
       vars_order = c("case_p.z", "death_p.z", "cv13.z", "risk_r.z", "covrac.z")) %>% 
  relabel_predictors(
        c(
            case_p.z = "County Covid Case %",
            death_p.z = "County Death Case %",
            cv13.z = "Covid-Related Life Events",
            risk_r.z = "Race-Related Covid Risk",
           covrac.z = "Covid-Induced Racism"
        )) + theme_classic() + scale_color_aaas(name = "Outcomes",
        labels = c("Fear of Covid", "Psychological Distress", "Psychological Health Change")) + labs(title = "Predicting Negative Psychological Health Outcomes") + xlab("Standardized Estimates") + theme(plot.title = element_text(face = "bold", hjust = 0.5),  legend.position = "top", legend.text = element_text(size = 8) ) 


```

```{r}


lancet <- c('#00468bff',	'#ED0000FF',	'#42B540FF',	'#0099B4FF',
'#925E9FFF',	'#FDAF91FF', '#AD002AFF',	'#ADB6B6FF',	
'#1B1919FF',	'#B09C85FF')



plot_summs(fear.z, distress.z, psyh.z, 
           model.names = c("Fear of Covid", "Psychological Distress", "Psychological Health Change"), coefs = c(
            "County Covid Case %" = "case_p.z",
            "County Death Case %" = "death_p.z" ,
            "Covid-Related Life Events" ="cv13.z" ,
            "Race-Related Covid Risk" ="risk_r.z" ,
           "Covid-Induced Racism" ="covrac.z" ), legend.title = "Outcomes", colors = lancet, point.shape=FALSE, point.size = 6) +labs(title = "Predicting Negative Psychological Health Outcomes") +  xlab("Standardized Estimates") + theme_classic() + theme(plot.title = element_text(face = "bold", hjust = 0.5), axis.title.y = element_blank(), axis.title.x = element_text(face = "bold"), legend.position = "top", legend.text = element_text(size = 8) )

```

I prefer the dotwhisker package to the jtools only because it provides more customization. For example, here i cannot really change the whisker size or dot shape. But given that both of these plotting functions are based on ggplot2, so if I created the plots in ggplot2, it might provide the optimal customization. 