---
title: "Portfolio 7 Ant Colony Optimization"
author: "Colin Li"
date: "3/28/2023"
output: github_document
---

Background: My thesis is a scale development project where in study 1 I used IRT and CFA to select best 6 belonging items from a pool of items. These are traditional psychometric approaches to creating short scales. But I heard there are modern machine learning algorithms can do that. Ant Colony Optimization is one of them. So
I wanted to see if using this method would result in the same 6 items that we selected from using the traditional psychometric methods. 

```{r}

library(ShortForm)
library(haven)

ant <- read_sav("C:/Users/Colin/Documents/ant.sav")

```

```{r}

antModel = ' Belong =~ Bi1 + BiBPS + Bi3 + Bi9 + Bi11 + Bi12 + Bi15 + Bi16 + Bi17 + Bi18 + Bi23 + Bi24 + Bi26 + Bi27 + Bi28 + Bi29 + Bi30 +'

list.items <- 
  list(c(
  "Bi1",
"BiBPS",
"Bi3",
"Bi9",
"Bi11",
"Bi12",
"Bi15",
"Bi16",
"Bi17",
"Bi18",
"Bi23",
"Bi24",
"Bi26",
"Bi27",
"Bi28",
"Bi29",
"Bi30"))

abilityShortForm <- antcolony.lavaan(
  data = ant,
  ants = 20, evaporation = 0.8, antModel = antModel,
  list.items = list.items, full = 17, i.per.f = 6,
  factors = "Belong", steps = 50, fit.indices = c("cfi", "tli", "rmsea", "srmr"),
  fit.statistics.test = "(cfi > 0.95)&(tli > 0.95)&(rmsea < 0.06)&(srmr<0.08)",  
                   max.run = 1000)


abilityShortForm
plot(abilityShortForm, type = 'pheromone')

```
Conclusion: I still don't quite understand how to set up all the parameters. And not sure whether this method is superior than traditional psychometric approaches. But 5 out of the resulting 6 items are the same as what we got by using CFA & IRT. 
