---
title: "Portfolio 8 some hisograms and density plots"
author: "Colin Li"
date: "4/13/2023"
output: github_document
---

Background: I'm told that it is helpful to look at each item's histogram when creating a scale. 

```{r}

library(psych)
library(ggplot2)
library(haven)
library(data.table)
library(ggridges)
library(ggsci)


```

```{r}

Be <- read_sav("C:/Users/Colin/Documents/PO8.sav")

multi.hist(Be[,sapply(Be, is.numeric)], freq = TRUE, bcol = "#79af97", breaks = 15, main = c("Item 1", "Item 2", "Item 3 (R)", "Item 4"))


```

```{r}

ggplot(Be, aes(x = Be1)) + geom_histogram(fill = "#79af97", color = "black") + theme_classic() + labs(title = "Item 1") + theme(plot.title = element_text(face = "bold", hjust = 0.5), axis.title.x = element_blank(), axis.title.y = element_blank()) 

ggplot(Be, aes(x = Be2)) + geom_histogram(fill = "#79af97", color = "black") + theme_classic() + labs(title = "Item 2", xlab = "") + theme(plot.title = element_text(face = "bold", hjust = 0.5), axis.title.x = element_blank(), axis.title.y = element_blank()) 

ggplot(Be, aes(x = BeR)) + geom_histogram(fill = "#79af97", color = "black") + theme_classic() + labs(title = "Item 3 (R)", xlab = "") + theme(plot.title = element_text(face = "bold", hjust = 0.5), axis.title.x = element_blank(), axis.title.y = element_blank()) 

ggplot(Be, aes(x = Be3)) + geom_histogram(fill = "#79af97", color = "black") + theme_classic() + labs(title = "Item 4", xlab = "") + theme(plot.title = element_text(face = "bold", hjust = 0.5), axis.title.x = element_blank(), axis.title.y = element_blank()) 


```

I would like to draw a normal curve for each histogram but it looks like I have to change it to density plot first. 

```{r}


Be_A <- melt(Be, measure.vars = c("Be1","Be2","BeR", "Be3"),
     variable.name = "Belong", value.name="Score")

Be_A$Belong <- factor(Be_A$Belong, levels = c("Be1", "Be2", "BeR", "Be3"),
                  labels = c("Item 1", "Item 2", "Item 3 (R)", "Item 4")
                  )
 
ggplot(Be_A, aes(x = Score)) + geom_histogram(fill = "#79af97", color = "black") + theme_classic() + theme(plot.title = element_text(face = "bold", hjust = 0.5), axis.title.x = element_blank(), axis.title.y = element_blank()) + facet_wrap(~ Belong) + theme(strip.background = element_blank(), strip.text = element_text(size = 10, face = "bold"))

```

```{r}

ggplot(Be_A, aes(x = Score, y = Belong, fill = stat(x))) +
  geom_density_ridges_gradient(bandwidth = 0.4) +
  scale_fill_gradient(name = "Range") + coord_cartesian(clip = "off") +
  theme_classic() + scale_x_continuous(limit = c(1, 5)) 

```
It's cool to have all the density plot together but then I feel like the continuous scale is kinda useless, i.e., the color change means nothing really. I was also having trouble of naming the legend. 

```{r}

ggplot(Be_A, aes(x = Score, y = Belong, fill = stat(x))) + geom_density_ridges_gradient(bandwidth = 0.4) +
  scale_fill_viridis_c(name = "Range", limits=c(1, 5), breaks=seq(1,5,by=1))  + coord_cartesian(clip = "off") +
  theme_classic() + scale_x_continuous(limit = c(1, 5)) + labs(title = "Data Distribution of A Short College Belonging Scale") + theme(plot.title = element_text(face = "bold", hjust = 0.5))

```
I really like the final look. 

```{r}

ggplot(Be_A, aes(x = Score, y = Belong, fill = Belong)) +   geom_density_ridges(fill = "#79af97", alpha = 0.5, bandwidth = 0.4) +
  theme_classic() + scale_x_continuous(limit = c(1, 5)) + labs(title = "Data Distribution of A Short College Belonging Scale") + theme(plot.title = element_text(face = "bold", hjust = 0.5))


```
