---
title: "Po 2- Violin and scatter plots"
author: "Colin Li"
date: "1/24/2023"
output: 
  html_document: 
    highlight: monochrome
    theme: cerulean
    toc: yes
    toc_float: yes
    number_sections: yes
---

# Load packages and t-test results
```{r filter}
library(haven)
library(dplyr)
require(ggiraph)
require(ggiraphExtra)
require(plyr)
library(ggsci)
library(ggplot2)
library(gridExtra)
library(effsize)
library(ggpubr)
Adata <- read_sav("C:/Users/Colin/Documents/GitHub/Colin_portfolio/p02/data/AQ.sav")
Bd <- Adata %>% 
  filter(Asian == "1")

t.test(Bd$Asian_Warmth~Bd$Conditions)

t.test(Bd$White_Warmth~Bd$Conditions)


#This study used a mixed design.
#We measured participants positive attitudes to toward Asians and Whites before and after the condition.
#Participants are Asian Americans. 
#The condition is whether being rejected by Asian or White peers. 
#I excluded people who do not identify as Asian Americans.
#Here, I only examine the between condition attitude difference.
#That is, compared to being rejected by Whites, do they feel have less positive attitude toward Asians when they are rejected by Asians?
#That is, compared to being rejected by Asians, do they feel have less positive attitude toward Whites when they are rejected by Whites?
```


# Plots
## Ingroup vs. outgroup prejudice on Asian Warmth

Asians who are rejected by Asians feel less warm toward Asians, compared to being rejected by Whites

```{r Ingroup Prejudice on Ingroup}
ggplot(data = Bd, 
       mapping = aes(x = Conditions, 
                     y = Asian_Warmth, fill = Conditions)) +
  geom_violin() +  stat_summary(fun = "mean",
               geom = "point", 
               width = 0.5,
               colour = "black") + stat_summary(fun.data = "mean_cl_normal",
               geom = "errorbar",
               width = .4) +
  scale_fill_jco()+theme(
  panel.background = element_rect(fill = NA),
  panel.grid.major = element_line(colour = "grey"))+
   scale_y_continuous(limit = c(0, 10))+
  stat_compare_means(method = "t.test", na.rm = TRUE) + xlab("Condition") + 
  ylab("Asian Warmth") +
  labs(caption = "t(180) = -2.66, 95% CI [-0.97, -0.14], Cohen's d = -0.39") + ggtitle("Ingroup Prejudice Negatively Affects Ingroup Attitude")

```


### for people who prefer bar graphs


```{r}
ggplot(Bd, aes(x= Conditions, y = Asian_Warmth)) +
  geom_bar(aes(fill = Conditions), stat = "summary", fun.y = "mean") + scale_y_continuous(limit = c(0, 10)) +  stat_summary(fun = "mean",
               geom = "point", 
               width = 0.5,
               colour = "black") + stat_summary(fun.data = "mean_cl_normal",
               geom = "errorbar",
               width = .4) +
  scale_fill_jco()+ theme(
  panel.background = element_rect(fill = NA),
  panel.grid.major = element_line(colour = "grey"))+
   scale_y_continuous(limit = c(0, 10))+
  stat_compare_means(method = "t.test", na.rm = TRUE) + xlab("Condition") + 
  ylab("Asian Warmth") +
  labs(caption = "t(180) = -2.66, 95% CI [-0.97, -0.14], Cohen's d = -0.39") + ggtitle("Ingroup Prejudice Negatively Affects Ingroup Attitude")



```


## Ingroup vs. outgroup prejudice on White Warmth

Asians who are rejected by Whites feel the same toward Whites, compared to being rejected by Asians


```{r Outgroup Prejudice on Outgroup}
ggplot(data = Bd, 
       mapping = aes(x = Conditions, 
                     y = White_Warmth, fill = Conditions)) +
  geom_violin() + stat_summary(fun = "mean",
               geom = "point", 
               width = 0.5,
               colour = "black") + stat_summary(fun.data = "mean_cl_normal",
               geom = "errorbar",
               width = .4) +
  scale_fill_jco()+theme(
  panel.background = element_rect(fill = NA),
  panel.grid.major = element_line(colour = "grey"))+
   scale_y_continuous(limit = c(0, 10))+
  stat_compare_means(method = "t.test", na.rm = TRUE) + xlab("Condition") + 
  ylab("White Warmth") + 
  labs(caption = "t(179) = -.32, 95% CI [-0.61, 0.44], Cohen's d = -0.05") + ggtitle("Prejudice Type Had No Effect on Outgroup Attitude")

```

### for people who prefer bar graphs


```{r}
ggplot(Bd, aes(x= Conditions, y = White_Warmth)) +
  geom_bar(aes(fill = Conditions), stat = "summary", fun.y = "mean") + scale_y_continuous(limit = c(0, 10)) +  stat_summary(fun = "mean",
               geom = "point", 
               width = 0.5,
               colour = "black") + stat_summary(fun.data = "mean_cl_normal",
               geom = "errorbar",
               width = .4) +
  scale_fill_jco()+ theme(
  panel.background = element_rect(fill = NA),
  panel.grid.major = element_line(colour = "grey"))+
   scale_y_continuous(limit = c(0, 10))+
  stat_compare_means(method = "t.test", na.rm = TRUE) + xlab("Condition") + 
  ylab("White Warmth") +
  labs(caption = "t(179) = -.32, 95% CI [-0.61, 0.44], Cohen's d = -0.05") + ggtitle("Prejudice Type Had No Effect on Outgroup Attitude")
```




## Prejudice type * centrality interaction

### Prejudice type * centrality interaction on Asian warmth

The impact of prejudice type (ingroup vs. outgroup) on positive attitude toward Asians does not differ by centrality (i.e., how much Asians value their group membership)

```{r Condition Centrality Interaction on Asian Warmth}


ggplot(data = Bd, 
       mapping = aes(x = Centrality, 
                     y = Asian_Warmth, color=Conditions)) +
  xlab("Centrality") + 
  ylab("Asian Warmth") + 
  geom_point() +
  scale_color_jco()+
  geom_smooth(method = lm)+ theme(
  panel.background = element_rect(fill = NA),
  panel.grid.major = element_line(colour = "grey"),
)+
   scale_y_continuous(limit = c(1, 10)) + ggtitle("The Impact of Prejudice Type Does Not Differ by Centrality")


```


### Prejudice type * centrality interaction on White warmth


The impact of Asian prejudice type (ingroup vs. outgroup) on positive attitude toward Whites does not differ by centrality (i.e., how much Asians value their group membership)

```{r Condition Centrality Interaction on White Warmth}
ggplot(data = Bd, 
       mapping = aes(x = Centrality, 
                     y = White_Warmth, color=Conditions)) +
  xlab("Centrality") + 
  ylab("White Warmth") +
  geom_point() +
  scale_color_jco()+
  geom_smooth(method = lm)+ theme(
  panel.background = element_rect(fill = NA),
  panel.grid.major = element_line(colour = "grey"),
)+
   scale_y_continuous(limit = c(1, 10)) + ggtitle("The Impact of Prejudice Type Does Not Differ by Centrality")


```




## Backup plots

These are backup plots for the violin plots


```{r}

#library(dplyr)
#library(magrittr)

Bd1 <- Bd %>% select(Conditions, Asian_Warmth, White_Warmth)


ggstatsplot::ggbetweenstats(
  data = Bd1, 
  x = Conditions, 
  y = Asian_Warmth,
  messages = FALSE) + scale_y_continuous(limit = c(0, 10))+ xlab("Condition") + 
  ylab("Asian Warmth") + scale_color_jco()+theme(
  panel.background = element_rect(fill = NA),
  panel.grid.major = element_line(colour = "grey"))

ggstatsplot::ggbetweenstats(
  data = Bd1, 
  x = Conditions, 
  y = White_Warmth,
  messages = FALSE) + scale_y_continuous(limit = c(0, 10))+ xlab("Condition") + 
  ylab("White Warmth") + scale_color_jco()+theme(
  panel.background = element_rect(fill = NA),
  panel.grid.major = element_line(colour = "grey"))

```


## fun plot

I won't use this graph, but I just think it's cool


```{r}

AW=lm(Asian_Warmth~Conditions*Centrality,Bd)
summary(AW)

ggPredict(AW,colorAsFactor = TRUE,interactive=TRUE) 

```