---
title: "Portfolio 6 Power"
author: "Colin Li"
date: "3/28/2023"
output: github_document
---

```{r}
library(pwrss)
library(haven)
library(tidyverse)

Adata <- read_sav("C:/Users/Colin/Documents/GitHub/Colin_portfolio/p02/data/AQ.sav")
Bd <- Adata %>% 
  filter(Asian == "1")

t.test(Bd$Asian_Warmth~Bd$Conditions)

```

I found a cool package that can visualize power as long as you provide the testing statistics and df. The red curve shows the null hypothesis, whereas the blue curve shows the alternative hypothesis. I wish I could change the legend theme, but I tried the code that works for ggplot won't work for this plot. 

```{r}

power.t.test(ncp = -2.6589, df = 179.97, alpha = 0.05, alternative = "not equal") 


```

the statistics for the plot below come from another study where I ran a planned contrast. Again, this is useful because published papers all have to show these statistics, so we can visualize their power whenever we want.  

```{r}

power.f.test(ncp = 6.49, df1 = 1, df2 = 7257, alpha = 0.05, plot = TRUE)

```


