---
title: "correlation matrix and tables"
author: "Colin Li"
date: "2/16/2023"
output: github_document
---


# Nice Looking Tables
```{r}
library(haven)
library(formattable)
library(data.table)
library(tidyverse)
library(dplyr)
library(knitr)
library(kableExtra)

fit <- read_csv("C:/Users/Colin/Documents/socfit.csv")

customGreen0 = "#DeF7E9"

customGreen = "#71CA97"

formattable(fit, align =c("l","c", "c", "c", "c","c","c","r"), list(
  `Model` = formatter("span", style = ~ formattable::style(color = "black", font.weight = "bold"), x ~ icontext(ifelse(x != "", "thumbs-up", ""), x)), 
  `Chi-Square`= color_tile(customGreen0, customGreen), 
  `P-Value`= color_tile(customGreen, customGreen0)))


fi2 <- read_csv("C:/Users/Colin/Documents/semfit.csv")

formattable(fi2, align =c("l","c", "c", "c", "c","c","c","r"), list(
  `Model` = formatter("span", style = ~ formattable::style(color = "black", font.weight = "bold"), x ~ icontext(ifelse(x != "", "thumbs-up", ""), x)), 
  `Chi-Square`= color_tile(customGreen0, customGreen), 
  `P-Value`= color_tile(customGreen, customGreen0)))




```

# Correlation Matrix
```{r}
library(ggplot2)
library(corrplot)
library(ggstatsplot)
library(ggsci)
library(ggcorrplot)

co <- read_sav("C:/Users/Colin/Documents/belong2.sav")

corr <- cor(co, use = "pairwise")


#testRes = cor.mtest(co, conf.level = 0.95)

#corrplot(corr, method="color", col=col(200),  type="upper", order="hclust", addCoef.col = "black", tl.col="black", tl.srt=45, sig.level = 0.01, insig = "blank", diag=FALSE)

ggcorrmat(co, cor.vars = c(Belonging, gpa, swl, se, mh, mil_pre, mil_search), 
  cor.vars.names = c(
    "College Belonging",
    "GPA",
    "Life Satisfaction",
    "Self-Esteem",
    "Mental Health",
    "Meaning in Life (Presence)",
    "Meaning in Life (Searching)"), p.adjust.method = "none")



col <- colorRampPalette(c("#BB4444", "#EE9988", "#FFFFFF", "#77AADD", "#4477AA"))



colors <- c('#E64B35FF',	'#4DBBD5FF',	'#00A087FF',	'#3C5488FF',
'#F39B7FFF',	'#8491B4FF', '#91D1C2FF',	'#DC0000FF',	
'#7E6148FF',	'#B09C85FF')



ggcorrplot(corr,
  type = "upper",
  insig = "blank",
  lab = TRUE,
  digits = 2, colors = c("#E69F00", "white", "#009E73"), ggtheme=ggstatsplot::theme_ggstatsplot())



